Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2018-07-12 AnalyticStructure_main.tex
Update on Overleaf.

\begin{figure}
\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
\end{figure}
Hence, contrary to GS, \emph{for LR calculation,
even when the response density is localized, the contribution coming from the 
continuum sector of the excitations can never be neglected}. 
In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
in the essential part of the Liouvillian spectrum.
This fact shows that it is \emph{impossible} to restrict the spectral representation
of $\chi(\omega)$ only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.

>>>>

\begin{figure}
\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
\end{figure}
Hence, contrary to GS, \emph{for LR calculation,
even when the response density is localized, the contribution coming from the 
continuum sector of the excitations can never be neglected}. 
In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
in the essential part of the Liouvillian spectrum.
This fact shows that it is \emph{impossible} to restrict the spectral representation
of $\chi(\omega)$ only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
